---
title: "part3"
output: html_document
---


## R Markdown
---
title: "part3"
output: html_document
---



## R Markdown
This part of data exploration will mainly deal with data in date-time format,and plotting the data for visualization. This skill will come in handy when dealing with time series analysis. 
#1. Sections: Introduction, Prerequisites, Creating Date / Times, From Strings, From Individual Components, From other types; Exercises: 3 
3)
```{r}
mdy(d1)

ymd(d2)

dmy(d3)

mdy(d4)

mdy(d5)
```


#2. Sections: Date Time Components, Getting Components, Rounding, Setting Components; Exercises:  2, 3, 4, 5
2)
```{r}
flights_dt %>%
  mutate(dep_time_ = sched_dep_time + dep_delay * 60) %>%
  filter(dep_time_ != dep_time) %>%
  select(dep_time_, dep_time, sched_dep_time, dep_delay)
```
The dep_time = sched_dep_time + dep_delay considering that there was consistency.

3)
```{r}
flights_dt %>%
  mutate(
    flight_duration = as.numeric(arr_time - dep_time),
    air_time_mins = air_time,
    diff = flight_duration - air_time_mins
  ) %>%
  select(origin, dest, flight_duration, air_time_mins, diff)
```

4) sched_dep_time should be used because it is used when booking a flight. 
dep_time can be afffected by other factors such as delays.

5)
```{r}
flights_dt %>%
  mutate(dow = wday(sched_dep_time)) %>%
  group_by(dow) %>%
  summarise(
    dep_delay = mean(dep_delay),
    arr_delay = mean(arr_delay, na.rm = TRUE)
  ) %>%
  print(n = Inf)
```
The lowest average departure delay time was recorded on Saturday hence the best day to travel.


#3. Sections: Time Spans, Durations, Periods, Intervals; Exercises: 3, 5
3)
#A vector of the first day of the month for every month in 2015:
```{r}
ymd("2015-01-01") + months(0:11)
```

# vector of dates giving the first day of every month in the current year.
```{r}
floor_date(today(), unit = "year") + months(0:11)
```

#4. Sections: Time Zones; No Exercise