---
title: "Part1EDA"
output: html_document
---

## R Markdown
#Sections: Introduction, Prerequisites, First Steps, The mpg Data Frame, Creating a ggplot, A Graphing Template

#Exercises: 1, 2 (Read it as mpg and not mtcars), 3,4, 5
#Introduction
1)
```{r}
library("tidyverse")
ggplot(data = mpg)
```
An empty plot is produced with the x and y axis.

2)
```{r}
Str(mpg)
```
There are 234 rows and 11 columns

3)
```{r}
?mpg
```
drv is a categorical variable.

4)Scatterplot of hwy vs cyl
```{r}
ggplot(mpg, aes(x = cyl, y = hwy)) +
  geom_point()
```

5)Scaterplot of class vs drv
```{r}
ggplot(mpg, aes(x = class, y = drv)) +
  geom_point()
```
The scatterplot has only a few points on it because we used a categorical variable


#Sections: Aesthetic Mappings

#Exercises: 1, 2, 3, 5, 6
1)
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```
The colour agrument is included in the mapping arguments hence treated as an aesthetic parameter.

2)
```{r}
str(mpg)
```
The categorical variables are manufacturer,model,trans,drv,fl,class

The continuos variables are displ,year,cyl,cty,hwy

3)Mapping a continuous variable to color,size and shape.
```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) +
  geom_point()
```
The continuous variable uses a scale.
 
In the case where the variable is used for size, the sizes of the points vary continuously with respect to their sizes.

```{r}
ggplot(mpg, aes(x = displ, y = hwy, size = cty)) +
geom_point()
```

When mapped to shape it gives an error as shown below.
```{r}
ggplot(mpg, aes(x = displ, y = hwy, shape = cty)) +
geom_point()
```

4)
```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = hwy, size = displ)) +
  geom_point()
```
A plot is produced.

5) Stroke changes the size of the border for shapes as shown below.
```{r}
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(shape = 21, colour = "black", fill = "white", size = 5, stroke = 5)
```

6)
```{r}
ggplot(mpg, aes(x = displ, y = hwy, colour = displ < 5)) +
  geom_point()
```
ggplot() displ<5 evaluates to true or false hence giving distinct categories of True or false.


#Sections: Common Problems, Facets
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)
```
It appears like dimensions are ignored when faceting.

4)
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```
when the number of categories increase, there is no much difference in the colors.

5)
```{r}
?facet_wrap
```
nrow is the number of rows and ncol the number of columns desired.
A grid lacks nrow and ncol because they are automatically specified automatically by the attributes used.
The nrow and ncol are not that important for facet_grid().



#Sections: Geometric Objects

#Exercises: 2, 5, 6
2)
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, colour = drv)) +
  geom_point() +
  geom_smooth(se = FALSE)
```
A scatterplot is produced with displ on the x-axis and hwy on the y-axis. The plot is colored with drv.

5)
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth()

ggplot() +
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```
The two plots will look the same because we are using the same mapping and data.

6)
```{r}
install.packages("gridExtra")
install.packages("cowplot")
library(cowplot)
```
The graphs are as shown below
```{r}
GraphA <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() +
  geom_smooth(se = FALSE)
  
GraphB<- ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() +
  geom_smooth(mapping = aes(group = drv), se = FALSE)
  
GC <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color=drv)) + 
  geom_point() +
  geom_smooth(se = FALSE)
  
GD <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color=drv)) +
  geom_smooth(se = FALSE)
  
GE <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color=drv)) +
  geom_smooth(se = FALSE, mapping = aes(linetype = drv))
  
GF <- ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color=drv)) + 
  geom_point(shape = 21, color = "white", stroke = 1)
theme_set(theme_gray())
plot_grid(GA, GB, GC, GD,GE,GF, labels=c("GA","GB","GC", "GD","GE","GF"), ncol=2, nrow = 3)
```


#Sections: Statistical Transformations

#Exercises: 1, 2, 5
1)The default for stats_summmary() is geom_pointrange()
```{r}
ggplot(data = diamonds) +
  geom_pointrange(
    mapping = aes(x = cut, y = depth),
    stat = "summary"
  )
```

2) Geom_col and geom_bar both have different default stat. Stat_identity is the default stat of geom_col while for geom_bar is stat_count.

5) Not including group=1 will, all the bars will be of equal height of 1.
 
 
 #Sections: Position Adjustments

#Exercises: 1, 2, 3
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
geom_point()
```
There is an overplotting problem. We can use the jitter position adjustment to solve the problem.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point(position = "jitter")
```

2)
```{r}
?geom_jitter()
```
The parameters are width ad heigth.

3) geom_jitter() vs geom_count()
geom_gitter introduces random variation to the points while geom_count sizes the points according to the number of the observations.


#Sections: Coordinate Systems

#Exercises: 1, 3, 4
1)A pie chart is made by applying the polar coordinates to a stacked bar chart.
```{r}
ggplot(mpg, aes(x = factor(1), fill = fl)) +
  geom_bar()
```

```{r}
ggplot(mpg, aes(x = factor(1), fill = fl)) +
  geom_bar(width = 1) +
  coord_polar(theta = "y")
```

3)coord_map uses the map projections to try fit the three dimensional earth to a 2D plane while coord_quickmap() uses an approximation map but faster projections.

4)
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```
The coord_fixed()ensures that geom_abline() produces a line at 45 degrees.

