---
title: "EDA technique part 2"
output: html_document
---

#R markdown
#Sections: Introduction, Prerequisites, Variation, Visualizing Distributions, Typical Values, Unusual Values
```{r}
library(tidyverse)
```

#Exercises:
1)Calculating the summary statistics for this variables that is x,y,z
```{r}
summary(select(diamonds, x, y, z))
```
#Then ploting histograms for each variable
```{r}
ggplot(diamonds) +
  geom_histogram(mapping = aes(x = x), binwidth = 0.01)

ggplot(diamonds) +
  geom_histogram(mapping = aes(x = y), binwidth = 0.01)

ggplot(diamonds) +
  geom_histogram(mapping = aes(x = z), binwidth = 0.01)
```

From the above we can clearly note that x and y seem to be larger than z.
Also there are outliers
The data in the variables are right skewed.
According to the documentation for the diamonds dataset, x is the length, y is the width and z is the depth.

2)Diamomds with price of 1,500 between 1,455 and $1,545. There also appears that a bulge distribution around diamonds worth 750.
```{r}
ggplot(filter(diamonds, price < 2500), aes(x = price)) +
  geom_histogram(binwidth = 10, center = 0)

ggplot(filter(diamonds), aes(x = price)) +
  geom_histogram(binwidth = 100, center = 0)
```

```{r}
diamonds %>%
  mutate(ending = price %% 100) %>%
  ggplot(aes(x = ending)) +
  geom_histogram(binwidth = 1)
```

3)
1 carat diamonds appear to be more than seventy times that of 0.99 carat diamond.
```{r}
diamonds %>%
  filter(carat >= 0.99, carat <= 1) %>%
  count(carat)
```
I believe that some diamonds are being rounded up this increases the price.

4) The coord_cartesian() function zooms that is specified by the limits specified.
```{r}
ggplot(diamonds) +
  geom_histogram(mapping = aes(x = price)) +
  coord_cartesian(xlim = c(100, 5000), ylim = c(0, 3000))
```

Before the calculation of the stats related to the histogram, the xlim() and ylim() functions influence actions. Before calculating the bin widths and counts, 
the values outside x and Y limits are dropped.
```{r}
ggplot(diamonds) +
  geom_histogram(mapping = aes(x = price)) +
  xlim(100, 5000) +
  ylim(0, 3000)
```

#Missing variables
When the number of observations is being calculated in an histogram, the missing values are removed and a warning message is displayed to notify you.
```{r}
diamonds2 <- diamonds %>%
  mutate(y = ifelse(y < 3 | y > 20, NA, y))

ggplot(diamonds2, aes(x = y)) +
  geom_histogram()
```
In the bar charts, NA is treated as a category.
```{r}
diamonds %>%
  mutate(cut = if_else(runif(n()) < 0.1, NA_character_, as.character(cut))) %>%
  ggplot() +
  geom_bar(mapping = aes(x = cut))
```

2) na.rm=TRUE removes NA values before calculating mean and sum.

#Sections: Covariation, A categorical and Continuous Variable

#Exercises: 2, 3, 5, 6
2) We can ignore the dimensions of the diamond since carat also measures size. We choose variables like carat,clarity,color and cut.
Since price and carat are continuous variables, we can plot them.
```{r}
ggplot(diamonds, aes(x = carat, y = price)) +
  geom_point()
```
It appears that there are so many points hence a boxplot by binning carat would be of help.
```{r}
ggplot(data = diamonds, mapping = aes(x = carat, y = price)) +
  geom_boxplot(mapping = aes(group = cut_width(carat, 0.1)), orientation = "x")
```
There appear to be a weak negative relationship between the color and price variable. Reverse the color levels to plot them in an increasing order of quality.
```{r}
diamonds %>%
  mutate(color = fct_rev(color)) %>%
  ggplot(aes(x = color, y = price)) +
  geom_boxplot()
```
As shown below there is also a weak negative correlation between clarity and price.
```{r}
ggplot(data = diamonds) +
  geom_boxplot(mapping = aes(x = clarity, y = price))
```
Clarity and color appear to have a larger amount of variation within the cateories more than between the categories.

In the above, we have found out that carat is the best predictor for price.

3) 
```{r}
install.packages("ggstance")
```
We can create the distribution of hwy and class using the geom_boxplot() function as before and then using the coord_flip()
```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = reorder(class, hwy, FUN = median), y = hwy)) +
  coord_flip()

library("ggstance")

ggplot(data = mpg) +
  geom_boxploth(mapping = aes(y = reorder(class, hwy, FUN = median), x = hwy))
```
In both cases the plottings look the same.

5)geom_violin() vs geom_histogram() vs colored geom_feqpoly().
plots using each function are as follows.
```{r}
#Using the frewpoly() function
ggplot(data = diamonds, mapping = aes(x = price, y = ..density..)) +
  geom_freqpoly(mapping = aes(color = cut), binwidth = 500)
#Using the histogram() function
ggplot(data = diamonds, mapping = aes(x = price)) +
  geom_histogram() +
  facet_wrap(~cut, ncol = 1, scales = "free_y")
#Using the violin() function
ggplot(data = diamonds, mapping = aes(x = cut, y = price)) +
  geom_violin() +
  coord_flip()

```
The geom_freqpoly() appears better for look ups.That is given y it is easy to tell x variable.
The geom_violin() and faceted geom_histogram() have almost the same strength and weaknesses.

6)
```{r}
install.packages("ggbeeswarm")
```
The similar method of the ggbeeswarm and geom_jitter() include are as follows.
  1)geom_quasirandom() which produces a mix of jitter and violin plots.
  2)geom_beeswarm() produces plots similar to violin plots through offsetting the points.
  
#Sections: Two Categorical Variables

#Exercises: 1,2
1) To show the distribution of cut within color we will have to create a new variable of proportion of each cut within a color using a grouped mutate.
```{r}
diamonds %>%
  count(color, cut) %>%
  group_by(color) %>%
  mutate(proportion = n / sum(n)) %>%
  ggplot(mapping = aes(x = color, y = cut)) +
  geom_tile(mapping = aes(fill = proporion))
```
To scale by distribution of color with cut we proceed as follows.
```{r}
diamonds %>%
  count(color, cut) %>%
  group_by(cut) %>%
  mutate(proportion = n / sum(n)) %>%
  ggplot(mapping = aes(x = color, y = cut)) +
  geom_tile(mapping = aes(fill = proportion))
```
2)
```{r}
flights %>%
  group_by(month, dest) %>%
  summarise(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(month), y = dest, fill = dep_delay)) +
  geom_tile() +
  labs(x = "Month", y = "Destination", fill = "Departure Delay")
```
In order to improve it we can try sorting the destinations by meaning full quantities for example the number of flights.

#Sections: Two Continuous Variables

#Exercises: 2, 4, 5
2)  Distribution of carat partitioned by price using a boxplot.
```{r}
ggplot(diamonds, aes(x = cut_number(price, 10), y = carat)) +
  geom_boxplot() +
  coord_flip() +
  xlab("Price")
```

4)Combined distribution of cut, carat and price.
```{r}
ggplot(diamonds, aes(x = carat, y = price)) +
  geom_hex() +
  facet_wrap(~cut, ncol = 1)
```
Also we can visualize it like:
```{r}
ggplot(diamonds, aes(colour = cut_number(carat, 5), y = price, x = cut)) +
  geom_boxplot()
```