---
title: "part 3"
output: html_document
---


#R markdown
#Sections: Introduction, Prerequisites, Variation, Visualizing Distributions, Typical Values, Unusual Values
```{r}
library(tidyverse)
```

#Exercises:
1) Summary statistics for this variables that is x,y,z
```{r}
summary(select(diamonds, x, y, z))
```
#Then ploting histograms for each variable
```{r}
ggplot(diamonds) +
  geom_histogram(mapping = aes(x = x), binwidth = 0.01)

ggplot(diamonds) +
  geom_histogram(mapping = aes(x = y), binwidth = 0.01)

ggplot(diamonds) +
  geom_histogram(mapping = aes(x = z), binwidth = 0.01)
```

x and y seem to be larger than z, there is also outliers and also data in the variables are right skewed.x is the length, y is the width and z is the depth.

2)By filtering the pricess less than 2500, there is a bulge distribution around diamonds worth 750.
```{r}
ggplot(filter(diamonds, price < 2500), aes(x = price)) +
  geom_histogram(binwidth = 10, center = 0)

ggplot(filter(diamonds), aes(x = price)) +
  geom_histogram(binwidth = 100, center = 0)
```

```{r}
diamonds %>%
  mutate(ending = price %% 100) %>%
  ggplot(aes(x = ending)) +
  geom_histogram(binwidth = 1)
```

3)
0.99 carat diamond appear to be less costly than 1 carat diamonds.
```{r}
diamonds %>%
  filter(carat >= 0.99, carat <= 1) %>%
  count(carat)
```

4) The limits apecify the coord_cartesian() function.
```{r}
ggplot(diamonds) +
  geom_histogram(mapping = aes(x = price)) +
  coord_cartesian(xlim = c(100, 5000), ylim = c(0, 3000))
```

The xlim() and ylim() functions influence actions,before the calculation of the stats related to the histogram.Before calculating the bin widths and counts,the values outside x and Y limits are dropped.
```{r}
ggplot(diamonds) +
  geom_histogram(mapping = aes(x = price)) +
  xlim(100, 5000) +
  ylim(0, 3000)
```

#Missing variables
The missing values are automatically removed when in an histogram and a warning message is displayed to notify you.
```{r}
diamonds2 <- diamonds %>%
  mutate(y = ifelse(y < 3 | y > 20, NA, y))

ggplot(diamonds2, aes(x = y)) +
  geom_histogram()
```

NA is treated as a category in the bar charts.
```{r}
diamonds %>%
  mutate(cut = if_else(runif(n()) < 0.1, NA_character_, as.character(cut))) %>%
  ggplot() +
  geom_bar(mapping = aes(x = cut))
```

2) na.rm=TRUE removes NA values before calculating mean and sum.

#Sections: Covariation, A categorical and Continuous Variable

#Exercises: 2, 3, 5, 6
2) Carat also measures size. We choose variables like carat,clarity,color and cut.

We can plot carat and prices to get more insight of the variables.
```{r}
ggplot(diamonds, aes(x = carat, y = price)) +
  geom_point()
```

Plotting a boxplot by binning carat would be of help due to the many points.
```{r}
ggplot(data = diamonds, mapping = aes(x = carat, y = price)) +
  geom_boxplot(mapping = aes(group = cut_width(carat, 0.1)), orientation = "x")
```

From the plots,there is a weak negative relationship between the color and price.
```{r}
diamonds %>%
  mutate(color = fct_rev(color)) %>%
  ggplot(aes(x = color, y = price)) +
  geom_boxplot()
```

There is also a weak negative correlation between clarity and price.
```{r}
ggplot(data = diamonds) +
  geom_boxplot(mapping = aes(x = clarity, y = price))
```
Carat appears to be the best predictor for price.

3) 
```{r}
install.packages("ggstance")
```

Plotting hwy and class using the geom_boxplot() function using the coord_flip()
```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = reorder(class, hwy, FUN = median), y = hwy)) +
  coord_flip()

library("ggstance")

ggplot(data = mpg) +
  geom_boxploth(mapping = aes(y = reorder(class, hwy, FUN = median), x = hwy))
```
The above plots look the same.

5) Plotting using the three functions.
```{r}
#Using the frewpoly() function
ggplot(data = diamonds, mapping = aes(x = price, y = ..density..)) +
  geom_freqpoly(mapping = aes(color = cut), binwidth = 500)
#Using the histogram() function
ggplot(data = diamonds, mapping = aes(x = price)) +
  geom_histogram() +
  facet_wrap(~cut, ncol = 1, scales = "free_y")
#Using the violin() function
ggplot(data = diamonds, mapping = aes(x = cut, y = price)) +
  geom_violin() +
  coord_flip()

```
The geom_freqpoly() appears better for look ups.That is given y it is easy to tell x variable.
The geom_violin() and faceted geom_histogram() have almost the same strength and weaknesses.

6)
```{r}
install.packages("ggbeeswarm")
```
The similar method of the ggbeeswarm and geom_jitter()
  1)geom_quasirandom() produces a mix of jitter and violin plots.
  2)geom_beeswarm() produces plots similar to violin plots through offsetting the points.
  
#Sections: Two Categorical Variables

#Exercises: 1,2
1) A new variable of proportion is created to show the distribution between cut within color using a grouped mutate.
```{r}
diamonds %>%
  count(color, cut) %>%
  group_by(color) %>%
  mutate(proportion = n / sum(n)) %>%
  ggplot(mapping = aes(x = color, y = cut)) +
  geom_tile(mapping = aes(fill = proporion))
```

Scaling the distribution of color with cut is as shown below.
```{r}
diamonds %>%
  count(color, cut) %>%
  group_by(cut) %>%
  mutate(proportion = n / sum(n)) %>%
  ggplot(mapping = aes(x = color, y = cut)) +
  geom_tile(mapping = aes(fill = proportion))
```
2)
```{r}
flights %>%
  group_by(month, dest) %>%
  summarise(dep_delay = mean(dep_delay, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(month), y = dest, fill = dep_delay)) +
  geom_tile() +
  labs(x = "Month", y = "Destination", fill = "Departure Delay")
```
To improve we can try getting rid of missing variables.


#Sections: Two Continuous Variables

#Exercises: 2, 4, 5
2)  Distribution of carat partitioned by price using a geom_boxplot().
```{r}
ggplot(diamonds, aes(x = cut_number(price, 10), y = carat)) +
  geom_boxplot() +
  coord_flip() +
  xlab("Price")
```

4)Combined distribution of cut, carat and price.
```{r}
ggplot(diamonds, aes(x = carat, y = price)) +
  geom_hex() +
  facet_wrap(~cut, ncol = 1)
```

Another way to visualize is as shown below
```{r}
ggplot(diamonds, aes(colour = cut_number(carat, 5), y = price, x = cut)) +
  geom_boxplot()
```